### 2014-04-23 article.tex
P1: Start filling in some of the sections, particularly intro/cal.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=10cm]{geogg101_screenshots/practical1/combined_meshes}
    \caption{Mesh generated for the Fowey Estuary, with a close-up of two sections. The main mesh shows the boundary conditions for both of the rivers in \SI{}{m/s} in red, as well as the initial water level at the sea boundary shown in \SI{}{m} in blue.}
    \label{fig:combined_meshes}
\end{figure}

@@

\begin{itemize}
    \item The Fowey Estuary is a macrotidal Estuary that is suitable for being modelled by a two-dimensional shallow water model.
    \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.03 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m/s}.
    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m/s} at the Berth, and \SI{0.10}{m/s} at the Inlet.
    \item Dredging the Estuary would have little to no effect further upstream of the dredged channel.
\end{itemize}

@@

\section{Introduction}
The Karup catchment is \SI{440}{km^2} \parencite{refsgaard1997parameterisation}.
MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refshaard1995mike}. It can be coupled to MIKE 11, which models one-dimensional water flow through channels \parencite{havno1995mike}. Wetlands can be effectively simulated by MIKE SHE \parencite{thompson2004simulation}.

@@

@@

\subsubsection{Precipitation}

@@

As can be seen in Table \ref{tab:summary_stats}, \dots

\begin{table}[!h]
    \centering
    \begin{tabular}{l c c c}
	    & RMSE & NSE & R \\
	    \hline
	Borehole 1 & 0.1 & 0.9 & 0.8 \\
	Borehole 2 & 0.1 & 0.9 & 0.8 \\
	Borehole 3 & 0.1 & 0.9 & 0.8 \\
	Borehole 4 & 0.1 & 0.9 & 0.8 \\
	    \hline
	Karup & 0.1 & 0.9 & 0.8 \\
	Hagebro & 0.1 & 0.9 & 0.8 \\
    \end{tabular}
    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.}
    \label{tab:summary_stats}
\end{table}

>>>>

\begin{figure}[hbp]
    \centering
    \includegraphics[width=10cm]{geogg101_screenshots/practical1/combined_meshes}
    \caption{Mesh generated for the Fowey Estuary, with a close-up of two sections. The main mesh shows the boundary conditions for both of the rivers in \SI{}{m.s^{-1}} in red, as well as the initial water level at the sea boundary shown in \SI{}{m} in blue.}
    \label{fig:combined_meshes}
\end{figure}

@@

\begin{itemize}
    \item The Fowey Estuary is a macrotidal Estuary that is suitable for being modelled by a two-dimensional shallow water model.
    \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.03 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m/s}.
    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
    \item Dredging the Estuary would have little to no effect further upstream of the dredged channel.
\end{itemize}

@@

The purpose of this study is to calibrate and validate a model of the Karup Catchment in Denmark. This model will then be used to simulate three future emissions scenarios of climate change in 2050: Low, Medium and High.

The Karup Catchment is \SI{440}{km^2}. It is situated in western Denmark and drains into the Limfjord. Geologically, it consists of highly permeable sand and gravel as well as occasionaly lenses of clay. 
The majority of land use is for agriculture (67\%), with forest (18\%), heath (10\%), wetland (4\%) and urban (1\%) making up the remainder \parencite{refsgaard1997parameterisation}.

% TODO: Location map of Karup in Denmark + locations of boreholes/rivers.

MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refsgaard1995mike, refsgaard2010systeme}. It can model precipitation, surface runoff, evapotsranspiration, and saturated zone and unsaturated zone subsurface flow. It can be coupled to MIKE 11, which models one-dimensional water flow through channels by solving the Saint Venant equations \parencite{havno1995mike}.  
It uses a finite difference approach to modelling catchments, and  and can be used with various spatially distributed characteristics such as elevation, land use and soil type. Additionally, the precipitation and evapotsranspiration can be specified for each grid cell in the model \parencite{thompson2012modelling}.

% TODO: Mike she schematic figure (maybe from thompson2004application).

@@

\subsubsection{Topology}

@@

\subsubsection{Precipitation and evapotsranspiration}

@@

As can be seen in Table \ref{table:summary_stats}, \dots

MIKE SHE is typically calibrated by modifying the parameters listed in Table \ref{table:calibration_parameters} \parencite{refsgaard1997parameterisation, thompson2004simulation}.

\begin{table}[!h]
    \centering
    \label{table:calibration_parameters}
    \begin{tabular}{l c c}
	Parameter   & Minimum \SI{}{m.s^{-1}} & Maximum \SI{}{m.s^{-1}} \\
	    \hline
	    Horizontal hydraulic condictivity of sand aquifer  & \num{1e-4} & \num{9e-4} \\
	    Vertical hydraulic condictivity of sand aquifer    & \num{1e-5} & \num{9e-5} \\
	    Horizontal hydraulic condictivity of clay lenses   & \num{1e-6} & \num{9e-6} \\
	    Vertical hydraulic condictivity of clay lenses     & \num{1e-7} & \num{9e-7} \\
    \end{tabular}
    \caption{Calibration parameters and the range of appropriate values.}
\end{table}

Using the split-sample method of \textcite{klemevs1986operational}.

\begin{table}[!h]
    \centering
    \label{table:summary_stats}
    \begin{tabular}{l c c c c c c}
	& \multicolumn{3}{c}{Calibration} & \multicolumn{3}{c}{Validation} \\
		    & RMSE & NSE  & R    & RMSE & NSE  & R    \\
	    \hline
	Borehole 5  & 0.19 & 0.63 & 0.82 & 0.23 & 0.52 & 0.77 \\
	Borehole 35 & 0.25 & 0.78 & 0.89 & 0.19 & 0.87 & 0.95 \\
	Borehole 37 & 0.23 & 0.55 & 0.81 & 0.13 & 0.81 & 0.91 \\
	Borehole 65 & 0.26 & 0.69 & 0.84 & 0.18 & 0.90 & 0.95 \\
	    \hline
	Karup       & 0.16 & 0.95 & 0.98 & 0.17 & 0.97 & 0.99 \\
	Hagebro     & 0.06 & 0.92 & 0.97 & 0.07 & 0.92 & 0.97 \\

    \end{tabular}
    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers. The calibration period was from 1971 to 1975 and the validation period was from 1976 to 1981.}
\end{table}
